\documentclass[11pt]{article}

% Use nice margins
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage[largesmallcaps]{kpfonts}
\usepackage[utf8]{inputenc}

% Use links
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={David Reed Resume},
  pdfauthor={David Reed}
}

\setlength{\parindent}{0em}

\begin{document}

% Get rid of page numbers
\thispagestyle{empty}

% Heading
\begin{center}
  {\LARGE\textsc{\textbf{David Reed}}}
\end{center}
\begin{center}
  \href{mailto:ddavidreed@gmail.com}{ddavidreed@gmail.com} • \href{http://www.davidjreed.net/}{www.davidjreed.net} • +1 (978) 914--0627 \\
  \hrulefill
\end{center}



\section*{\textsc{Professional Experience}}
\begin{itemize}
\item \textbf{Software Engineer} at \textbf{Virtyx Technologies} --- Quincy, MA \hfill {\em January 2017--August 2017}
  \begin{itemize}
  \item Designed, developed, tested, and deployed software for the Virtyx endpoint monitoring system using Java, AngularJS 2, Spring, PostgreSQL, Golang, Python, and Node.js.
  \item Leveraged automatic testing, linting, and deployment through Jenkins.
  \item Created RESTful API endpoints using Java and Spring.
  \item Interfaced with 3rd--party APIs to better gather data on publicly-known IPs.
  \item Developed and tested web-scraping and geolocation services.
  \item Communicated with team members to best architect new systems as customer needs evolved.
  \item Investigated and resolved testing issues from operating system and CPU architecture differences.
  \item Created operating system-specific utility parsers for Ping, Traceroute, and DiG using regular expressions in Java.
  \item Improved PostgreSQL interaction efficiency by 90\% with more efficient SQL usage.
  \item Developed and implemented end-to-end testing with database integration.
  \end{itemize}
\end{itemize}



\section*{\textsc{Education}}
\begin{itemize}
\item \textbf{B.S. Comp. Sci. and Mathematics Candidate} \hfill \textit{\textbf{Northeastern University}} --- Boston, MA \\ \em{Dean's List}, 3.4 \textsc{g.p.a.} with Honors \hfill {\em September 2015--Present}
  \begin{itemize}
  \item Object-Oriented Development
  \item Web Development
  \item Computer Systems
  \item Algorithms
  \item Theory of Computation
  \item Probability and Statistics
  \item Linear Algebra and Differential Equations
  \item Calculus I, II, III
  \end{itemize}
\end{itemize}



\section*{\textsc{Technical Skills}}
\begin{itemize}
\item \textbf{Proficient:} JavaScript (Node.js and browser), Java, HTML, CSS, git
\item \textbf{Familiar:} Python, PostgreSQL, shell scripting, AngularJS, Sass, Spring, Golang, GNU Make
  \item \textbf{Acquainted:} C, LaTeX, Docker, MySQL, D3.js, Nginx, Scheme
\end{itemize}



\section*{\textsc{Certifications and Honor Societies}}
\begin{itemize}
\item Certified First-Aid Provider
\item Certified Open-Water SCUBA Diver
\end{itemize}

\end{document}
